---
title: "732A54 - Big Data Analytics - Lab RDB"
author: "Julius Kittler (julki092) and Maximilian Pfundstein (maxpf364)"
date: "`r Sys.Date()`"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
  html_document:
    df_print: paged
    number_sections: no
    toc: yes
    toc_float: no
  word_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
```

# SQL-Statements

## Statement 1

1) List all employees, i.e. all tuples in the jbemployee relation.

```{mysql, eval = FALSE, echo = TRUE}
SELECT * FROM jbemployee
```

```{r}
csv1 = read.csv2("task1.csv", sep = ",")
kable(csv1)
```

## Statement 2

2) List the name of all departments in alphabetical order. Note: by “name” we mean the name attribute for all tuples in the jbdept relation.

```{mysql, eval = FALSE, echo = TRUE}
SELECT name FROM jbdept ORDER BY name
```

```{r}
csv2 = read.csv2("task2.csv", sep = ",")
kable(csv2)
```

## Statement 3

3) What parts are not in store, i.e. qoh = 0? (qoh = Quantity On Hand)

```{mysql, eval = FALSE, echo = TRUE}
SELECT name FROM jbparts WHERE qoh = 0 ORDER BY name
```

```{r}
csv3 = read.csv2("task3.csv", sep = ",")
kable(csv3)
```

## Statement 4

4) Which employees have a salary between 9000 (included) and 10000 (included)?

```{mysql, eval = FALSE, echo = TRUE}
SELECT name FROM jbemployee WHERE salary >= 9000 AND salary <= 10000
  ORDER BY name
```

```{r}
csv4 = read.csv2("task4.csv", sep = ",")
kable(csv4)
```

## Statement 5

5) What was the age of each employee when they started working (startyear)?

```{mysql, eval = FALSE, echo = TRUE}
SELECT *, (startyear-birthyear) AS "Age When Started" FROM jbemployee
```

```{r}
csv5 = read.csv2("task5.csv", sep = ",")
kable(csv5)
```

## Statement 6

6) Which employees have a last name ending with 'son'?

```{mysql, eval = FALSE, echo = TRUE}
SELECT * FROM jbemployee WHERE SUBSTRING_INDEX(name, ',', 1) LIKE '%son';
```

```{r}
csv6 = read.csv2("task6.csv", sep = ";")
kable(csv6)
```

## Statement 7

7) Which items (note items, not parts) have been delivered by a supplier called Fisher-Price? Formulate this query using a subquery in the where-clause.

```{mysql, eval = FALSE, echo = TRUE}
SELECT * FROM jbitem WHERE supplier IN
  (SELECT id from jbsupplier WHERE name = "Fisher-Price")
```

```{r}
csv7 = read.csv2("task7.csv", sep = ",")
kable(csv7)
```

## Statement 8

8) Formulate the same query as above, but without a subquery.

```{mysql, eval = FALSE, echo = TRUE}
SELECT * FROM jbitem INNER JOIN jbsupplier ON jbitem.supplier = jbsupplier.id
  WHERE jbsupplier.name = "Fisher-Price"
```

```{r}
csv8 = read.csv2("task8.csv", sep = ",")
kable(csv8)
```

## Statement 9

9) Show all cities that have suppliers located in them. Formulate this query using a
subquery in the where-clause.

```{mysql, eval = FALSE, echo = TRUE}
SELECT * FROM jbcity WHERE jbcity.id IN (SELECT city FROM jbsupplier)
```

```{r}
csv9 = read.csv2("task9.csv", sep = ",")
kable(csv9)
```

## Statement 10

10) What is the name and color of the parts that are heavier than a card reader?
Formulate this query using a subquery in the where-clause. (The SQL query must
not contain the weight as a constant.)

```{mysql, eval = FALSE, echo = TRUE}
SELECT name, color FROM jbparts WHERE weight > (SELECT weight FROM jbparts
                                                  WHERE name = "card reader")
```

```{r}
csv10 = read.csv2("task10.csv", sep = ",")
kable(csv10)
```

## Statement 11

11) Formulate the same query as above, but without a subquery. (The query must not
contain the weight as a constant.)

```{mysql, eval = FALSE, echo = TRUE}
SELECT parts1.name, parts1.color FROM jbparts AS parts1, jbparts AS parts2
  WHERE parts2.name = "card reader" AND parts1.weight > parts2.weight
```

```{r}
csv11 = read.csv2("task11.csv", sep = ",")
kable(csv11)
```

## Statement 12

12) What is the average weight of black parts?

```{mysql, eval = FALSE, echo = TRUE}
SELECT AVG(weight) FROM jbparts WHERE color = 'black'
```

```{r}
csv12 = read.csv2("task12.csv", sep = ",")
kable(csv12)
```

## Statement 13

13) What is the total weight of all parts that each supplier in Massachusetts (“Mass”) has delivered? Retrieve the name and the total weight for each of these suppliers. Do not forget to take the quantity of delivered parts into account. Note that one row should be returned for each supplier.

```{mysql, eval = FALSE, echo = TRUE}
SELECT jbsupplier.name, SUM(js.quan * jp.weight) AS total_weight FROM jbsupplier
  LEFT JOIN jbcity jc ON jbsupplier.city = jc.id
  LEFT JOIN jbsupply js ON jbsupplier.id = js.supplier
  LEFT JOIN jbparts jp on js.part = jp.id
  WHERE  jc.state = 'Mass'
  GROUP BY jbsupplier.id
```

```{r}
csv13 = read.csv2("task13.csv", sep = ",")
kable(csv13)
```

## Statement 14

14) Create a new relation (a table), with the same attributes as the table items using
the CREATE TABLE syntax where you define every attribute explicitly (i.e. not
as a copy of another table). Then fill the table with all items that cost less than the
average price for items. Remember to define primary and foreign keys in your
table!

```{mysql, eval = FALSE, echo = TRUE}
CREATE TABLE jbitem_custom (
    id INT,
    name VARCHAR(20),
    dept INT NOT NULL,
    price INT,
    qoh INT UNSIGNED,
    supplier INT,
    CONSTRAINT pk_item PRIMARY KEY(id),
    CONSTRAINT dept FOREIGN KEY(dept) REFERENCES jbdept(id),
    CONSTRAINT supplier FOREIGN KEY(supplier) REFERENCES jbsupplier(id));

INSERT INTO jbitem_custom (id, name, dept, price, qoh, supplier)
  SELECT ji.id, ji.name, ji.dept, ji.price, ji.qoh, ji.supplier
  FROM jbitem AS ji WHERE ji.price < (SELECT AVG(jbitem.price) FROM jbitem)
```
